Revisiting Multi-Domain Machine Translation

### 2020-08-27 2020/tacl2020/multidomain.tex
more changes in final sections

A third series of motivations are of statistical nature. The training data available for each domain is usually unevenly distributed, and domain-specific systems trained or adapted on small datasets are likely to have a high variance and generalize poorly. For some test domains, there may even be no data at all \cite{Farajian17neural}. Training mix-domain systems is likely to reduce this variance, at the expense of a larger statistical bias \cite{Clark12onesystem}. Under this view, MDMT would be especially beneficial for domains with little training data \revision{(see also \cite{Sharaf20metalearning} for a discussion of DA in low-resource conditions and a meta-learning based approach to this problem)}\fyTodo{Best place ?}. This is observed for multilingual MT from English: an improvement for under-resourced languages due to positive transfer, at the cost of a decrease in performance for well-resourced languages \cite{Arivazhagan19massively}.

Combining multiple domain-specific MTs can also be justified in the sake of distributional robustness \cite{Mansour09domainadaptation,Mansour09multiple}, for instance when the test mixture differs from the train mixture, or when it includes new domains unseen in training.
\sout{Such scenario is already well documented for zero-shot multilingual MT} \cite{Firat16multiway,Ha16towards,Johnson17google,Platanios18contextual}\sout{where mixing languages has more than demonstrated its usefulness.}
An even more challenging case is when the MT would need to perform well for any test distribution, as studied for statistical MT in \cite{Huck15mixeddomain}. In all these cases, mixing domains in training and/or testing is likely to improve robustness against unexpected or adversarial test distribution \cite{Oren19distributionally}.

@@

\subsection{Multi-domain systems should be effective \label{ssec:effective}}
% \subsubsection{Performance}
A first expectation is that MDMT systems should perform well in the face of mixed-domain test data. From this, we derive the following three requirements.

@@

\paragraph{[P4-ERR]}
A MDMT should perform best when the true domain tag is known, but deteriorate gracefully in the presence of tag errors; in this situation, catastrophic drops in performance can be observed\fyDone{cite \cite{McCloskey89catastrophic}}. This requirement can be assessed by translating test texts with erroneous domain tags and reporting the correlated decrease of performance.

@@

\begin{itemize}
\item a generic model trained on a concatenation of all corpora (\texttt{Mixed}). We develop two versions\footnote{In fact three: to enable a fair comparison with WDCMT, a RNN-based variant is also trained and evaluated. \revision{This system appears as \system{Mixed-Nat-RNN} in Table~\ref{tab:performance}}.} of this system, one where the domain unbalance reflects the distribution of our training data \revision{given in Table~\ref{tab:Corpora}} (\system{Mixed-Nat}) and one where all domains are equally represented in training (\system{Mixed-Bal}). The former is the best option when the train mixture $\mathcal{D}^s$ is also expected in testing; the latter should be used when the test distribution is uniform across domains. Accordingly, we report two aggregate scores: a weighted average reflecting the training distribution, and an unweighted average, meaning that test domains are equally important.
%   As explained above, depending whether MDMT are expected to perform specially well on large domains, or to treat all domains equally, one or the other training distribution should be prefered.\jcDone{All systems cand be learned following both Bal and Nat. does Nat corresponds to wAVG in test? is wAVG defined somewhere?}
\item fine-tuned models \cite{Luong15stanford,Freitag16fast}\jcDone{i would use Luong and Manning 2015}, based on the \system{Mixed-Nat} system, further trained on each domain for at most 20~000 iterations, with early stopping when the dev BLEU stops increasing. The full fine-tuning (\system{FT-Full}) procedure may update all the parameters of the initial generic model, resulting in six systems adapted for one domain, with no parameter sharing across domains.
\revisiondel{We again contrast two versions: full fine-tuning (\system{FT-Full}), which may update all the parameters of the initial generic model; and the variant of \cite{Bapna19simple}, where fine-tuning only updates a small adaptation module that is added (with residual connections) on top of every Transformer layer (\system{FT Res}).}
\end{itemize}

For all models, we set the embeddings size and the hidden layers size to~512. Transformers use multi-head attention with 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 cells. The multi-domain residual system (see description below) additionally uses an adaptation block in each transformer layer, composed of 2-layer perceptron, with an inner $\operatorname{ReLU}$ activation function operating on normalized entries of dimension~1024. 
% The gated variant is made of a dense layer, followed by a layer normalization and a sigmoid activation.
% The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.
Training use a batch size of~12,288 tokens; optimization uses Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$ and Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ for all layers.\fyDone{Describe the block adaptation layer - voir slides} 
% All our systems are implemented in OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein17opennmt}.

\subsection{Multi-domain systems \label{ssec:systems}}
\fyDone{Remove Gated residual}
Our comparison of multi-domain systems includes our own reimplementations of recent proposals from the literature:\footnote{\revision{Further implementation details are in Appendix~A.}}
\begin{itemize}
\item a system using domain control as in \cite{Kobus17domaincontrol}: domain information is introduced either as an additional token for each source sentence (\system{DC-Tag}), or introduced in the form of a supplementary feature for each word (\system{DC-Feat}).
\item a system using lexicalized domain representations \cite{Pham19generic}: word embeddings are composed of a generic and a domain specific part (\system{LDR});\fyDone{why not LDR as in Minh's paper?}
\item the three proposals of \newcite{Britz17mixing}. \system{TTM} is a feature-based approach where the domain tag is introduced as an extra word \textsl{on the target side}. Training uses reference tags and inference is usually performed with predicted tags, just like for regular target words. \system{DM} is a multi-task learner where a domain classifier is trained on top the MT encoder, so as to make it aware of domain differences; \system{ADM} is the adversarial version of \system{DM}, pushing the encoder towards learning domain-independent source representations. These methods thus only use domain tags in training.
\item \revision{two multi-domain versions of the approach of \newcite{Bapna19simple}, denoted \system{FT Res} and \system{MDL Res}, where a domain-specific adaptation module is added to all the Transformer layers; within each layer, residual connections enable to by-pass this module. The former variant corresponds to the original proposal of \citet{Bapna19simple} and fine-tunes the adapter modules of a \system{Mixed-Nat} system independently for each domain, keeping all the other parameters frozen. The latter is novel; it uses the same architecture, but a different training procedure, as all parameters are jointly learned from scratch from a mix-domain corpus. }
  % In a variant (\system{MDL Gated}), we use a gating mechanism to merge computations using the the adapter modules and with those that don not.
% the entire multi-domain system from scratch.\fyDone{Check this.}
\item the multi-domain model of \newcite{Zeng18multidomain} (\system{WDCMT}), where a domain-agnostic and a domain-specialized representation of the input are simultaneously processed; supervised classification and adversarial training are used to compute these representations. \revision{As for the three previous proposals, inference does not use domain tags.}\footnote{For this system, we use the available RNN-based system from the authors (\url{https://github.com/DeepLearnXMU/WDCNMT}\fyDone{URLs}) which does not directly compare to the other, Transformer-based, systems; the improved version of \cite{Su19exploring} seems to produce comparable, albeit slightly improved, results.}\fyDone{Check this}
\end{itemize}
\revision{Note that this list includes systems that slightly depart from our definition of MDMT: standard implementations of \system{TTM} and \system{WDCMT} rely on infered, rather than on gold, domain tags - which must somewhat affect their predictions; \system{DM} and {ADM} make no use of domain tags at all.} We however did not consider the proposal of \cite{Farajian17multidomain} which performs on-the-fly tuning for each test sentence and diverges more strongly from our notion of MDMT. % and should be able to handle available domain labels in training and testing.
% This system has shown to meet several of requirements and would also have no problem scaling to a large number of domains.\fyDone{TBC}

@@

Fine-tuning each domain separately provides us with a better baseline, outperforming \system{Mixed-Nat} for all domains, with significant gains for domains that are distant from \domain{med}: \domain{rel}, \domain{it}, \domain{bank}, \domain{law}.
% A complete fine-tuning, updating all parameters, proves more effective than only adapting a subpart of the network - a result that could be due to keeping fixed the capacity of the adapter module.
\fyDone{Add 2 averages ?}\fyDone{Significance testing wrt Mix Generic, Full Fine-tuned, for each domain}

All MDMTs (except \system{DM} and \system{ADM}) slightly improve over the generic baseline (for most domains), these improvements are rarely significant. \revision{Among systems using an extra domain feature, \system{DC-Tags} has a small edge over \system{DC-Feats} and also requires less paramaters; it also outperforms \system{TTM}, which however uses predicted rather than gold domain tags. \system{TTM} is also the best choice among the systems that to not use domain tags in inference.} \revision{The best contender overall are  \system{FT Res} and \system{MDL Res}, which significantly improve over \system{Mixed-Nat} for a majority of domains, and are the only ones to clearly fulfill [P1-LAB];} \system{WDCMT} also improves on three domains, but regresses on one. The use of a dedicated adaptation component, seems here to prove better than feature-based strategies; \revision{this comes at the cost of a large increase of the number of parameters.} The effect of the adaptation layer is especially significant for small domains (\domain{bank}, \domain{it} and \domain{rel}).

@@

All systems fail to outperform fine-tuning, sometimes by a wide margin, especially for an ``isolated'' domain like \domain{rel}. This might be due to the fact that domains are well separated (cf.\ Section~\ref{ssec:corpora}) and are hardly helping each other. In this situation, MDMT systems should instead make sure that each domain is allocated a sufficient number of parameters, so as to close the gap with fine-tuning.
\fyDone{More comments when we have all the results}\fyDone{Importance of sharing and unsharing}

@@

In the second (\domain{new}), we assess [P5-UNK] by translating sentences from a domain unseen in training (\domain{news}).\fyDone{i would use RND / UNK rather than OLD / NEW} For each sentence, we automatically predict the most likely domain tag and use it for decoding.\footnote{\revision{To automatically predict domain tags, we train a language model in each domain and assign tag on a per-sentence basis based the language model log-probability (assuming uniform domain priors). Our domain classifier has an average prediction error of 16.4\% for in-domain data.}}
% Results are in the rightmost column of Table~\ref{tab:redomains}.
In this configuration, again, systems using domain tags in the inference step perform poorly, significantly worse than the \system{Mixed-Nat} baseline (Bleu=23.5)\fyDone{performance drop is now measured against Mixed-nat (leave it clearer?)}, sometimes by a large margin.\fyDone{Check significance, To be completed}

\subsubsection{Handling growing numbers of domains}
Another set of experiments evaluate the ability to dynamically handle supplementary domains (requirement [P6-DYN]) as follows. Starting with the existing MD systems of Section~\ref{ssec:rawperformance}, we introduce an extra domain (\domain{News}) and resume training with this new mixture of data\footnote{The design of a proper balance between domains in training is critical for achieving optimal performance: as our goal is to evaluate all systems in the same conditions, we consider a basic mixing policy based on the new training distribution. This is detrimental to the small domains, for which the ``negative transfer'' effect is stronger than for larger domains.} for 50,000 additional iterations.\fyDone{Training regime of continuation} We contrast this approach with training all systems from scratch and report differences in performance in Table~\ref{tab:warmrestart}.\footnote{WDCMT results are excluded from this table, as resuming training proved difficult to implement.}\fyDone{Ecrire un commentaire} 
We expect that MDMT systems should not be too significantly impacted by the addition of a new domain and reach about the same performance as when training with this domain from scratch. From a practical viewpoint, dynamically integrating new domains is straightforward for \system{DC-Tag}, \system{DC-Feat} or \system{TTM}, for which new domains merely add new labels. It is less easy for \system{DM}, \system{ADM} and \system{WDCMT}, which include a built-in domain classifier whose outputs have to be pre-specified, or for \system{LDR}, \system{FT~Res} and \system{MDL~Res} for which the number of possible domains is built in the architecture and has to be anticipated from the start. This makes a difference between domain-bounded systems, for which the number of domains is limited and truly open-domain systems.% , which seamlessly integrate additional domains.

\begin{table*}
  \centering
  \begin{tabular}{|p{1.7cm}|*{9}{r|}} \hline
    \footnotesize
   \hfill Domain  Model \hfill & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{news}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \footnotesize\system{Mixed-Nat}  & 37.1  & 54.1  & 49.6	& 34.1  & 42.1	& 77.0 & 28.9 & 40.8	& 49.0 \\[-2pt]
                   & \sbcl{-0.2}{--}  &\sbcl{-0.5}{---} &\sbcl{-0.5}{--} &\sbcl{+0.6}{--} &\sbcl{-1.1}{--} &\sbcl{-6.5}{--} &\sbcl{+5.4}{--} &\sbcl{-0.3}{--} & \sbcl{-0.4}{--} \\
%    \system{Mixed-Nat}  & 37.3  & 54.6   & 50.1   & 33.5  & 43.2  & 77.5  & 23.5 & 41.1 & 49.4 \\
%    \system{FT-Full}       & 37.7  & 59.2   & 54.5   & 34.0  & 46.8  & 90.8  & **** & 42.8 & 53.8 \\
    \hline%\hline
    \footnotesize \system{DC-Tag}      &  37.7 & 54.5   & 49.9    &  34.8 &  43.9  & 78.8 & 29.5  & 41.4 & 49.9\\[-2pt]
%                                   & 38.0  & 54.4   & 49.2    & \SW{33.6}  &  \SW{42.7}  &\SW{75.3}  & \SW{28.1}  & & 48.9\\
                   & \sbcl{-0.4}{+0.3}  & \sbcl{-0.8}{-0.1}   & \sbcl{-0.1}{-0.6}  & \sbcl{+1.6}{\SW{-1.1}}  &  \sbcl{+0.4}{\SW{-1.3}}  & \sbcl{-1.7}{\SW{-3.5}}  & \sbcl{+7.7}{\SW{-1.4}}  & \sbcl{-0.2}{-0.1} & \sbcl{-0.2}{\SW{-1.2}}\\

    \footnotesize \system{DC-Feat}     & 37.4 & 54.9   & 50.0    & 34.7  &  43.9  & 79.6 & 28.9  & 41.2 & 50.1\\[-2pt]
%                   & 37.2 & 54.7   & 49.9    & 34.2  &  43.0  & 79.9 & \SW{28.1}  & &\\
                   & \scriptsize -0.2 & \scriptsize -0.1  & \scriptsize -0.1 & \scriptsize -0.6 & \scriptsize -0.9 & \scriptsize +0.3 & \scriptsize \SW{-0.8} & \scriptsize -0.2 & \scriptsize -0.3\\

    \footnotesize \system{LDR}    & 37.0   & 54.6  & 49.6    & 34.3  &  43.0  &77.0  & 28.7 & 40.8 & 49.2 \\[-2pt]
                    & \scriptsize -0.6 &	\scriptsize +0.5 & \scriptsize -0.4 & \scriptsize -0.6 &	\scriptsize +0.5 & \scriptsize +\SB{3.8} & \scriptsize \SW{-0.9} & \scriptsize +0.5 & \scriptsize -0.4 \\

    \footnotesize \system{TTM}           &  37.3 & 54.4   & 49.6    & 33.8  &  42.9  &78.2  & 29.1 & 41 & 49.4\\[-2pt]
%                   & 37.1  & 54.2   & 49.1    & \SW{32.8}  &  42.0  &\SW{74.2}  & \SW{27.7}& 48.2\\
                    & \scriptsize -0.3  & \scriptsize -0.3  & \scriptsize -0.5    & \scriptsize \SW{-1.1}  &  \scriptsize \SW{-1.0}  & \scriptsize \SW{-4.0}  & \scriptsize \SW{-1.4}& \scriptsize -0.5 & \scriptsize \SW{-1.2}\\

    \footnotesize \system{DM}            &36.0 &51.3&46.8&31.8&39.8&65.7&27.0 & 38.9 & 45.2\\[-2pt]
%                   &36.5&51.7&47.4&31.7&40.3&65.7&\SW{25.8}& & \\
                   & \scriptsize +0.6& \scriptsize +0.4& \scriptsize +0.6& \scriptsize -0.1& \scriptsize +0.5 & \scriptsize 0.0& \scriptsize \SW{-1.2}& \scriptsize +0.5 & \scriptsize +0.3\\

    \footnotesize \system{ADM}          &36.6&54.2&49.1&32.9&42.1&75.7&28.7 & 40.2 & 48.4 \\[-2pt]
%                   &  36.9 &53.5&48.3&32.7&41.7&\SW{70.7}&\SW{26.8}& \\
                   & \scriptsize +0.3 & \scriptsize -0.8 & \scriptsize -0.8 & \scriptsize -0.2 & \scriptsize -0.4 & \scriptsize \SW{-5.0} & \scriptsize \SW{-1.9} & \scriptsize -0.2 & \scriptsize \SW{-1.1}\\

>>>>

A third series of motivations are of statistical nature. The training data available for each domain is usually unevenly distributed, and domain-specific systems trained or adapted on small datasets are likely to have a high variance and generalize poorly. For some test domains, there may even be no data at all \cite{Farajian17neural}. Training mix-domain systems is likely to reduce this variance, at the expense of a larger statistical bias \cite{Clark12onesystem}. Under this view, MDMT would be especially beneficial for domains with little training data. This is observed for multilingual MT from English: an improvement for under-resourced languages due to positive transfer, at the cost of a decrease in performance for well-resourced languages \cite{Arivazhagan19massively}.

Combining multiple domain-specific MTs can also be justified in the sake of distributional robustness \cite{Mansour09domainadaptation,Mansour09multiple}, for instance when the test mixture differs from the train mixture, or when it includes new domains unseen in training.
\revisiondel{Such scenario is already well documented for zero-shot multilingual MT \cite{Firat16multiway,Ha16towards,Johnson17google,Platanios18contextual} where mixing languages has more than demonstrated its usefulness.}
An even more challenging case is when the MT would need to perform well for any test distribution, as studied for statistical MT in \cite{Huck15mixeddomain}. In all these cases, mixing domains in training and/or testing is likely to improve robustness against unexpected or adversarial test distribution \cite{Oren19distributionally}.

@@

\subsection{Multi-domain systems should be effective \label{ssec:effective}}
% \subsubsection{Performance}
A first expectation is that MDMT systems should perform well in the face of mixed-domain test data. We thus derive the following requirements.

@@

\paragraph{[P4-ERR]}
MDMTs should perform best when the true domain tag is known, but deteriorate gracefully in the face of tag errors; in this situation, catastrophic drops in performance are often observed\fyDone{cite \cite{McCloskey89catastrophic}}. This requirement can be assessed by translating test texts with erroneous domain tags and reporting the subsequent loss in performance.

@@

\begin{itemize}
\item a generic model trained on a concatenation of all corpora (\texttt{Mixed}). We develop two versions\footnote{In fact three: to enable a fair comparison with WDCMT, a RNN-based variant is also trained and evaluated. \revision{This system appears as \system{Mixed-Nat-RNN} in Table~\ref{tab:performance}}.} of this system, one where the domain unbalance reflects the distribution of our training data \revision{given in Table~\ref{tab:Corpora}} (\system{Mixed-Nat}) and one where all domains are equally represented in training (\system{Mixed-Bal}). The former is the best option when the train mixture $\mathcal{D}^s$ is also expected in testing; the latter should be used when the test distribution is uniform across domains. Accordingly, we report two aggregate scores: a weighted average reflecting the training distribution, and an unweighted average, meaning that test domains are equally important.
%   As explained above, depending whether MDMT are expected to perform specially well on large domains, or to treat all domains equally, one or the other training distribution should be prefered.\jcDone{All systems cand be learned following both Bal and Nat. does Nat corresponds to wAVG in test? is wAVG defined somewhere?}
\item fine-tuned models \cite{Luong15stanford,Freitag16fast}\jcDone{i would use Luong and Manning 2015}, based on the \system{Mixed-Nat} system, further trained on each domain for at most 20~000 iterations, with early stopping when the dev BLEU stops increasing. The full fine-tuning (\system{FT-Full}) procedure may update all the parameters of the initial generic model, resulting in six systems adapted for one domain, with no parameter sharing across domains.
\revisiondel{We again contrast two versions: full fine-tuning (\system{FT-Full}), which may update all the parameters of the initial generic model; and the variant of \cite{Bapna19simple}, where fine-tuning only updates a small adaptation module that is added (with residualconnections) on top of every Transformer layer (\system{FT-Res}).}
\end{itemize}

All models use embeddings and the hidden layers sizes of dimension~512. Transformers contain with 8 attention heads in each of the 6+6 layers; the inner feedforward layer contains 2048 cells. The adapter-based systems (see below) additionally use an adaptation block in each layer, composed of a 2-layer perceptron, with an inner $\operatorname{ReLU}$ activation function operating on normalized entries of dimension~1024. 
% The gated variant is made of a dense layer, followed by a layer normalization and a sigmoid activation.
% The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.
Training uses batches of~12,288 tokens, Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$, Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ in all layers.\fyDone{Describe the block adaptation layer - voir slides} 
% All our systems are implemented in OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein17opennmt}.

\subsection{Multi-domain systems \label{ssec:systems}}
\fyDone{Remove Gated residual}
Our comparison of multi-domain systems includes our own reimplementations of recent proposals from the literature:\footnote{\revision{Further implementation details are in Appendix~A.}}
\begin{itemize}
\item a system using domain control as in \cite{Kobus17domaincontrol}: domain information is introduced either as an additional token for each source sentence (\system{DC-Tag}), or as a supplementary feature for each word (\system{DC-Feat}).
\item a system using lexicalized domain representations \cite{Pham19generic}: word embeddings are composed of a generic and a domain specific part (\system{LDR});\fyDone{why not LDR as in Minh's paper?}
\item the three proposals of \newcite{Britz17mixing}. \system{TTM} is a feature-based approach where the domain tag is introduced as an extra word \textsl{on the target side}. Training uses reference tags and inference is usually performed with predicted tags, just like for regular target words. \system{DM} is a multi-task learner where a domain classifier is trained on top the MT encoder, so as to make it aware of domain differences; \system{ADM} is the adversarial version of \system{DM}, pushing the encoder towards learning domain-independent source representations. These methods thus only use domain tags in training.
\item the multi-domain model of \newcite{Zeng18multidomain} (\system{WDCMT}), where a domain-agnostic and a domain-specialized representation of the input are simultaneously processed; supervised classification and adversarial training are used to compute these representations. \revision{Again, inference does not use domain tags.}\footnote{For this system, we use the available RNN-based system from the authors (\url{https://github.com/DeepLearnXMU/WDCNMT}\fyDone{URLs}) which does not directly compare to the other, Transformer-based, systems; the improved version of \cite{Su19exploring} seems to produce comparable, albeit slightly improved, results.}\fyDone{Check this}
\item \revision{two multi-domain versions of the approach of \newcite{Bapna19simple}, denoted \system{FT-Res} and \system{MDL-Res}, where a domain-specific adaptation module is added to all the Transformer layers; within each layer, residual connections enable to by-pass this module. The former variant corresponds to the original proposal of \citet{Bapna19simple} \revision{(see also \cite{Sharaf20metalearning})}. It fine-tunes the adapter modules of a \system{Mixed-Nat} system independently for each domain, keeping all the other parameters frozen. The latter uses the same architecture, but a different training procedure and learns all parameters jointly from scratch with a mix-domain corpus.}
  % In a variant (\system{MDL Gated}), we use a gating mechanism to merge computations using the the adapter modules and with those that don not.
% the entire multi-domain system from scratch.\fyDone{Check this.}
\end{itemize}
\revision{This list includes systems that slightly depart from our definition of MDMT: standard implementations of \system{TTM} and \system{WDCMT} rely on infered, rather than on gold, domain tags - which must somewhat affect their predictions; \system{DM} and {ADM} make no use of domain tags at all.} We however did not consider the proposal of \cite{Farajian17multidomain} which performs on-the-fly tuning for each test sentence and diverges more strongly from our notion of MDMT. % and should be able to handle available domain labels in training and testing.
% This system has shown to meet several of requirements and would also have no problem scaling to a large number of domains.\fyDone{TBC}

@@

Fine-tuning each domain separately yields a better baseline, outperforming \system{Mixed-Nat} for all domains, with significant gains for domains that are distant from \domain{med}: \domain{rel}, \domain{it}, \domain{bank}, \domain{law}.
% A complete fine-tuning, updating all parameters, proves more effective than only adapting a subpart of the network - a result that could be due to keeping fixed the capacity of the adapter module.
\fyDone{Add 2 averages ?}\fyDone{Significance testing wrt Mix Generic, Full Fine-tuned, for each domain}

All MDMTs (except \system{DM} and \system{ADM}) slightly improve over \system{Mixed-Nat}(for most domains), but these gains are rarely significant. \revision{Among systems using an extra domain feature, \system{DC-Tag} has a small edge over \system{DC-Feat} and also requires less paramaters; it also outperforms \system{TTM}, which however uses predicted rather than gold domain tags. \system{TTM} is also the best choice among the systems that to not use domain tags in inference.} \revision{The best contenders overall are  \system{FT-Res} and \system{MDL-Res}, which significantly improve over \system{Mixed-Nat} for a majority of domains, and are the only ones to clearly fulfill [P1-LAB];} \system{WDCMT} also improves on three domains, but regresses on one. The use of a dedicated adaptation component, seems here better than feature-based strategies, \revision{but yields a large increase of the number of parameters.} The effect of the adaptation layer is especially significant for small domains (\domain{bank}, \domain{it} and \domain{rel}).

@@

All systems fail to outperform fine-tuning, sometimes by a wide margin, especially for an ``isolated'' domain like \domain{rel}. This might be due to the fact that domains are well separated (cf.\ Section~\ref{ssec:corpora}) and are hardly helping each other. In this situation, MDMT systems should dedicate a sufficient number of parameters to each domain, so as to close the gap with fine-tuning.
\fyDone{More comments when we have all the results}\fyDone{Importance of sharing and unsharing}

@@

In the second (\domain{new}), we assess [P5-UNK] by translating sentences from a domain unseen in training (\domain{news}).\fyDone{i would use RND / UNK rather than OLD / NEW} For each sentence, we automatically predict the domain tag and use it for decoding.\footnote{\revision{Domain tags are assigned as follows: we train a language model for each domain and assign tag on a per-sentence basis based the language model log-probability (assuming uniform domain priors). The domain classifier has an average prediction error of 16.4\% for in-domain data.}}
% Results are in the rightmost column of Table~\ref{tab:redomains}.
In this configuration, again, systems using domain tags during inference perform poorly, significantly worse than the \system{Mixed-Nat} baseline (Bleu=23.5)\fyDone{performance drop is now measured against Mixed-nat (leave it clearer?)}, sometimes by a large margin.\fyDone{Check significance, To be completed}

\subsubsection{Handling growing numbers of domains}
Another set of experiments evaluate the ability to dynamically handle supplementary domains (requirement [P6-DYN]) as follows. Starting with the existing MD systems of Section~\ref{ssec:rawperformance}, we introduce an extra domain (\domain{News}) and resume training with this new mixture of data\footnote{The design of a proper balance between domains in training is critical for achieving optimal performance: as our goal is to evaluate all systems in the same conditions, we consider a basic mixing policy based on the new training distribution. This is detrimental to the small domains, for which the ``negative transfer'' effect is stronger than for larger domains.} for 50,000 additional iterations.\fyDone{Training regime of continuation} We contrast this approach with training all systems from scratch and report differences in performance in Table~\ref{tab:warmrestart}.\footnote{WDCMT results are excluded from this table, as resuming training proved difficult to implement.}\fyDone{Ecrire un commentaire} 
We expect that MDMT systems should not be too significantly impacted by the addition of a new domain and reach about the same performance as when training with this domain from scratch. From a practical viewpoint, dynamically integrating new domains is straightforward for \system{DC-Tag}, \system{DC-Feat} or \system{TTM}, for which new domains merely add new labels. It is less easy for \system{DM}, \system{ADM} and \system{WDCMT}, which include a built-in domain classifier whose outputs have to be pre-specified, or for \system{LDR}, \system{FT-Res} and \system{MDL-Res} for which the number of possible domains is built in the architecture and has to be anticipated from the start. This makes a difference between domain-bounded systems, for which the number of domains is limited and truly open-domain systems.% , which seamlessly integrate additional domains.

\begin{table*}
  \centering
  \begin{tabular}{|p{1.6cm}|*{9}{r|}} \hline
    \footnotesize
   \hfill Domain  Model \hfill & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{news}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \footnotesize\system{Mixed-Nat}  & 37.1  & 54.1  & 49.6	& 34.1  & 42.1	& 77.0 & 28.9 & 40.8	& 49.0 \\[-2pt]
                   & \sbcl{+0.2}{--}  &\sbcl{+0.5}{---} &\sbcl{+0.5}{--} &\sbcl{-0.6}{--} &\sbcl{+1.1}{--} &\sbcl{+0.5}{--} &\sbcl{-5.4}{--} &\sbcl{+0.3}{--} & \sbcl{+0.4}{--} \\
%    \system{Mixed-Nat}  & 37.3  & 54.6   & 50.1   & 33.5  & 43.2  & 77.5  & 23.5 & 41.1 & 49.4 \\
%    \system{FT-Full}       & 37.7  & 59.2   & 54.5   & 34.0  & 46.8  & 90.8  & **** & 42.8 & 53.8 \\
    \hline%\hline
    \footnotesize \system{DC-Tag}      &  37.7 & 54.5   & 49.9    &  34.8 &  43.9  & 78.8 & 29.5  & 41.4 & 49.9\\[-2pt]
%                                   & 38.0  & 54.4   & 49.2    & \SW{33.6}  &  \SW{42.7}  &\SW{75.3}  & \SW{28.1}  & & 48.9\\
                   & \sbcl{+0.3}{+0.3}  & \sbcl{\SB{+0.8}}{-0.1}   & \sbcl{-0.04}{-0.6}  & \sbcl{\SW{-1.6}}{\SW{-1.1}}  &  \sbcl{-0.4}{\SW{-1.3}}  & \sbcl{\SB{+1.7}}{\SW{-3.5}}  & \sbcl{\SW{-7.7}}{\SW{-1.4}}  & \sbcl{+0.2}{-0.1} & \sbcl{+0.1}{\SW{-1.1}}\\

    \footnotesize \system{DC-Feat}     & 37.4 & 54.9   & 50.0    & 34.7  &  43.9  & 79.6 & 28.9  & 41.2 & 50.1\\[-2pt]
%                   & 37.2 & 54.7   & 49.9    & 34.2  &  43.0  & 79.9 & \SW{28.1}  & &\\
                   &  \sbcl{+0.3}{-0.2} & \sbcl{-0.1}{-0.1}  & \sbcl{-0.3}{-0.1} & \sbcl{\SW{-1.3}}{-0.6} & \sbcl{-0.1}{-0.9} & \scriptsize \sbcl{+0.4}{+0.3} & \sbcl{\SW{-7.3}}{\SW{-0.8}} & \sbcl{+0.1}{-0.2} & \sbcl{-0.2}{-0.3}\\

    \footnotesize \system{LDR}    & 37.0   & 54.6  & 49.6    & 34.3  &  43.0  &77.0  & 28.7 & 40.8 & 49.2 \\[-2pt]
                    & \sbcl{0.0}{-0.6} &  \sbcl{+0.1}{+0.5} & \sbcl{+0.2}{-0.4} &  \sbcl{-0.4}{-0.6} &  \sbcl{+0.5}{+0.5} & \sbcl{\SB{+2.9}}{+\SB{3.8}} & \sbcl{\SW{-6.6}}{\SW{-0.9}} & \sbcl{+0.6}{+0.5} &  \sbcl{+0.1}{-0.4} \\

    \footnotesize \system{TTM}           &  37.3 & 54.4   & 49.6    & 33.8  &  42.9  &78.2  & 29.1 & 41.0 & 49.4\\[-2pt]
%                   & 37.1  & 54.2   & 49.1    & \SW{32.8}  &  42.0  &\SW{74.2}  & \SW{27.7}& 48.2\\
                    & \sbcl{0.0}{-0.3}  & \sbcl{+0.4}{-0.3}  & \sbcl{-0.1}{-0.5}  & \sbcl{-0.9}{\SW{-1.1}}  & \sbcl{+0.6}{\SW{-1.0}}  & \sbcl{\SB{+1.8}}{\SW{-4.0}} & \sbcl{\SW{-5.7}}{\SW{-1.4}} & \sbcl{0.0}{-0.5} & \sbcl{+0.3}{\SW{-1.2}}\\

    \footnotesize \system{DM}            &36.0 &51.3&46.8&31.8&39.8&65.7&27.0 & 38.9 & 45.2\\[-2pt]
%                   &36.5&51.7&47.4&31.7&40.3&65.7&\SW{25.8}& & \\
                   & \sbcl{-0.4}{+0.6} & \sbcl{\SW{-1.8}}{+0.4} & \sbcl{\SW{-1.2}}{+0.6} & \sbcl{\SW{-1.8}}{-0.1} & \sbcl{\SW{-2.6}}{+0.5} & \sbcl{\SW{-3.3}}{0.0} & \sbcl{\SW{-4.4}}{\SW{-1.2}} & \sbcl{-0.8}{+0.5} & \sbcl{\SW{-1.8}}{+0.3}\\

    \footnotesize \system{ADM}          &36.6&54.2&49.1&32.9&42.1&75.7&28.7 & 40.2 & 48.4 \\[-2pt]
%                   &  36.9 &53.5&48.3&32.7&41.7&\SW{70.7}&\SW{26.8}& \\
                   & \sbcl{-0.2}{+0.3} & \sbcl{-0.7}{-0.8} & \sbcl{-0.8}{-0.8} & \sbcl{-0.9}{-0.2} & \sbcl{-0.5}{-0.4} & \sbcl{\SW{-2.3}}{\SW{-5.0}} & \sbcl{\SW{-5.4}}{\SW{-1.9}} & \sbcl{-0.5}{-0.2} & \sbcl{\SW{-0.9}}{\SW{-1.1}}\\

%    \system{WDCMT}     &&&&&&& & &\\[-2pt]
%                    &&&&&&&&& \\
    \footnotesize \revision{\system{FT Res}}  & 37.0 & 57.6 & 53.8 & 34.5 &	46.1 & 91.1 & 29.6 &	42.2  & 53.3 \\[-2pt]
                               & \sbcl{+0.3}{+0.3} & \sbcl{+0.4}{+0.4} & \sbcl{+0.1}{+0.1} & \sbcl{-0.7}{-0.7} & \sbcl{+0.5}{+0.5} & \sbcl{-0.9}{-0.9} & \sbcl{\SW{-9.0}}{-0.6} & \sbcl{-0.1}{-0.1} & \sbcl{+0.2}{+0.2} \\
